Chapter 4

### 2021-08-04 thesis_chapter_4.Rmd
more sites read-in

oude_winter <- tidync("OceanParcels/chapter_4_output/oudekraal_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_winter$season <- "Winter" 
oude_winter$site <- "Oudekraal" 
oude_wintermean <- oude_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_winter_mean$season <- "Winter" 
oude_winter_mean$site <- "Oudekraal"

oude_spring <- tidync("OceanParcels/chapter_4_output/oudekraal_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_spring$season <- "Spring" 
oude_spring$site <- "Oudekraal" 
oude_spring <- scar_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_spring_mean$season <- "Spring" 
oude_spring_mean$site <- "Oudekraal"

>>>>

oude_winter <- tidync("OceanParcels/chapter_4_output/oudekraal_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_winter$season <- "Winter" 
oude_winter$site <- "Oudekraal" 
oude_winter_mean <- oude_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_winter_mean$season <- "Winter" 
oude_winter_mean$site <- "Oudekraal"

oude_spring <- tidync("OceanParcels/chapter_4_output/oudekraal_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_spring$season <- "Spring" 
oude_spring$site <- "Oudekraal" 
oude_spring <- oude_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_spring_mean$season <- "Spring" 
oude_spring_mean$site <- "Oudekraal"

betty_summer <- tidync("OceanParcels/chapter_4_output/betty_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
betty_summer$season <- "Summer" 
betty_summer$site <- "Betty's Bay" 
betty_summer_mean <- betty_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
betty_summer_mean$season <- "Summer" 
betty_summer_mean$site <- "Betty's Bay"

betty_autumn <- tidync("OceanParcels/chapter_4_output/betty_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
betty_autumn$season <- "Autumn" 
betty_autumn$site <- "Betty's Bay" 
betty_autumn_mean <- betty_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
betty_autumn_mean$season <- "Autumn" 
betty_autumn_mean$site <- "Betty's Bay"

betty_winter <- tidync("OceanParcels/chapter_4_output/betty_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
betty_winter$season <- "Winter" 
betty_winter$site <- "Betty's Bay" 
betty_winter_mean <- betty_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
betty_winter_mean$season <- "Winter" 
betty_winter_mean$site <- "Betty's Bay"

betty_spring <- tidync("OceanParcels/chapter_4_output/betty_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
betty_spring$season <- "Spring" 
betty_spring$site <- "Betty's Bay" 
betty_spring_mean <- betty_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
betty_spring_mean$season <- "Spring" 
betty_spring_mean$site <- "Betty's Bay"

kalk_summer <- tidync("OceanParcels/chapter_4_output/kalk_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kalk_summer$season <- "Summer" 
kalk_summer$site <- "Kalk Bay" 
kalk_summer_mean <- kalk_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kalk_summer_mean$season <- "Summer" 
kalk_summer_mean$site <- "Kalk Bay"

kalk_autumn <- tidync("OceanParcels/chapter_4_output/kalk_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kalk_autumn$season <- "Autumn" 
kalk_autumn$site <- "Kalk Bay" 
kalk_autumn_mean <- kalk_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kalk_autumn_mean$season <- "Autumn" 
kalk_autumn_mean$site <- "Kalk Bay"

kalk_winter <- tidync("OceanParcels/chapter_4_output/kalk_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kalk_winter$season <- "Winter" 
kalk_winter$site <- "Kalk Bay" 
kalk_winter_mean <- kalk_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kalk_winter_mean$season <- "Winter" 
kalk_winter_mean$site <- "Kalk Bay"

kalk_spring <- tidync("OceanParcels/chapter_4_output/kalk_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
kalk_spring$season <- "Spring" 
kalk_spring$site <- "Kalk Bay" 
kalk_spring_mean <- kalk_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
kalk_spring_mean$season <- "Spring" 
kalk_spring_mean$site <- "Kalk Bay"

aframe_summer <- tidync("OceanParcels/chapter_4_output/aframe_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
aframe_summer$season <- "Summer" 
aframe_summer$site <- "A-Frame" 
aframe_summer_mean <- aframe_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
aframe_summer_mean$season <- "Summer" 
aframe_summer_mean$site <- "A-Frame"

aframe_autumn <- tidync("OceanParcels/chapter_4_output/aframe_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
aframe_autumn$season <- "Autumn" 
aframe_autumn$site <- "A-Frame" 
aframe_autumn_mean <- aframe_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
aframe_autumn_mean$season <- "Autumn" 
aframe_autumn_mean$site <- "A-Frame"

aframe_winter <- tidync("OceanParcels/chapter_4_output/aframe_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
aframe_winter$season <- "Winter" 
aframe_winter$site <- "A-Frame" 
aframe_winter_mean <- aframe_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
aframe_winter_mean$season <- "Winter" 
aframe_winter_mean$site <- "A-Frame"

aframe_spring <- tidync("OceanParcels/chapter_4_output/aframe_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
aframe_spring$season <- "Spring" 
aframe_spring$site <- "A-Frame" 
aframe_spring_mean <- aframe_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
aframe_spring_mean$season <- "Spring" 
aframe_spring_mean$site <- "A-Frame"

sthelena_summer <- tidync("OceanParcels/chapter_4_output/sthelena_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
sthelena_summer$season <- "Summer" 
sthelena_summer$site <- "St. Helena Bay" 
sthelena_summer_mean <- sthelena_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
sthelena_summer_mean$season <- "Summer" 
sthelena_summer_mean$site <- "St. Helena Bay"

sthelena_autumn <- tidync("OceanParcels/chapter_4_output/sthelena_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
sthelena_autumn$season <- "Autumn" 
sthelena_autumn$site <- "St. Helena Bay" 
sthelena_autumn_mean <- sthelena_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
sthelena_autumn_mean$season <- "Autumn" 
sthelena_autumn_mean$site <- "St. Helena Bay"

sthelena_winter <- tidync("OceanParcels/chapter_4_output/sthelena_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
sthelena_winter$season <- "Winter" 
sthelena_winter$site <- "St. Helena Bay" 
sthelena_winter_mean <- sthelena_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
sthelena_winter_mean$season <- "Winter" 
sthelena_winter_mean$site <- "St. Helena Bay"

sthelena_spring <- tidync("OceanParcels/chapter_4_output/sthelena_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
sthelena_spring$season <- "Spring" 
sthelena_spring$site <- "St. Helena Bay" 
sthelena_spring_mean <- sthelena_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
sthelena_spring_mean$season <- "Spring" 
sthelena_spring_mean$site <- "St. Helena Bay"
